---
title: "Group 07 CA pollution burden"
author: Grace Bianchi & Atefeh Mohseni
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attach packages
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r echo = TRUE, warning = FALSE, message = FALSE}
# read in the data
ces <- read_csv(here("data", "ces3demographics.csv")) %>%
  clean_names()
```

```{r echo = TRUE, warning = FALSE, message = FALSE}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() +
  labs(x = "% White population",
       y = "CES 3.0 Score",
       caption = "Data from 2010 Census") +
   geom_col(position = "fill") +
   scale_fill_gradient(low = "yellow", high = "red") + 
   theme_minimal()
```

**Figure 1. CalEnviroScreen 3.0 score versus percentage of the white residents.** Based on Figure 1, it seems that CES 3.0 Score and percentage of white residents are negatively correlated. This means neighborhoods with more diverse ethnicity (people of color) experience more collective environmental burdens, such as pollution. 

### Citation:
Wieland, W. 2018. CalEnviroScreen 3.0 Results. Office of Environmental Health Hazard Assessment.  https://data.ca.gov/dataset/calenviroscreen-3-0-results (Accessed 2021-11-14). 


